On the presentation of orthogonal groups over polynomial rings

### 2019-07-08 dl-paper.tex
Fix signs

Consider now the case when $\Phi$ is symplectic. In this case the assertion of the lemma is just a reformulation of~\cite[Theorem~B]{MR91},
which asserts that for $\ell \geq 1$ one has $\K_2(\rC_\ell, k[X, X\inv] \cong \K_2(\rC_\ell, k) \oplus P(k)$, where
$P(k)$ is the set $k^* \times I_2(k)$ with the group structure given by
\[ (u, y) \cdot (v, z) = (uv, y + z - \langle\langle u, v\rangle\rangle).\]
Here $I^2(k)$ stands for the second power of the fundamental ideal $I(k)$ in the Witt ring $W(k)$ of $k$.
Recall that $\K_1^\mathrm{MW}(k)$ is isomorphic to the pullback of the diagram:
\[ \xymatrix{ \K_1^\mathrm{MW}(k) \ar[r] \ar[d] & I(k) \ar[d] \\ \K_1(k) \ar[r] & I(k)/I^2(k), } \]
in other words, it consists of pairs $[u, x]$ such that $x - \langle \langle u \rangle \rangle \in I^2(k)$.
It is not hard to verify that tha map $[u, x] \mapsto (u, x - \langle\langle u \rangle\rangle)$ defines an isomorphism of $P(k)$ and $\K_1^\mathrm{MW}(k)$.

\begin{comment}
Under additonal assumption $\mathrm{char}(k)\neq 2$ the assertion of the lemma in the symplectic case can be obtained as a chain of isomorphisms
\[ \K_2(\rC_\ell, k[X, X\inv]) \cong \GW_2^2(\Phi, k[X, X\inv]) \cong \GW_2^2(k) \oplus \GW_1^1(k) \cong \K_2^\mathrm{MW}(k) \oplus \K_1^\mathrm{MW}(k). \]
Here the first 
corollary of~\cite[Lemma~4.1.1]{AF17} and \cref{bass-ft} below. 
\end{comment}
\end{proof}

>>>>

Consider now the case when $\Phi$ is symplectic. In this case the assertion of the lemma is just a reformulation of~\cite[Theorem~B]{MR91},
which asserts that for $\ell \geq 1$ one has $\K_2(\rC_\ell, k[X, X\inv] \cong \K_2(\rC_\ell, k) \oplus P(k)$, where
$P(k)$ is the set $k^* \times I_2(k)$ with the group structure given by
\[ (u, y) \cdot (v, z) = (uv, y + z - \langle\langle u, v\rangle\rangle).\]
Here $I^2(k)$ stands for the second power of the fundamental ideal $I(k)$ in the Witt ring $W(k)$ of $k$.
Recall that $\K_1^\mathrm{MW}(k)$ is isomorphic to the pullback of the diagram:
\[ \xymatrix{ \K_1^\mathrm{MW}(k) \ar[r] \ar[d] & I(k) \ar[d] \\ \K_1(k) \ar[r] & I(k)/I^2(k), } \]
in other words, it consists of pairs $[u, x]$ such that $x - \langle \langle u \rangle \rangle \in I^2(k)$.
It is easy to verify that the map $[u, x] \mapsto (u, \langle\langle u \rangle\rangle - x)$ defines an isomorphism of $\K_1^\mathrm{MW}(k)$ and $P(k)$. \end{proof}
